Measuring Political Freedom Around the World

### 2020-11-11 slides.Rmd
.

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE)
```

@@

class: center, top
<font size="1">
```{r results='asis',out.width='25%', fig.align='center'}
stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                     title = "Regression Results", 
                     covariate.labels = c(),header = FALSE,
single.row=FALSE,column.sep.width = "-15pt", column.separate = 1)
```

>>>>

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_slide_tone()
```

@@

class: center, top
<font size="1">
```{r results='asis',out.width='25%', fig.align='center',}
stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                     title = "Regression Results", 
                     covariate.labels = c(),header = FALSE,
single.row=FALSE,column.sep.width = "-15pt")
```
